---
title: "Exploration_music_data"
format: html
editor: visual
author: Alexander Staub
---

## Libraries & data loading

```{r message=FALSE}


if (!require(renv)) install.packages("renv"); library(renv) # environment creator package
if (!require(readr)) install.packages("readr"); library(readr) # reading csv files
if (!require(tidyverse)) install.packages("tidyverse"); library(tidyverse) # tidyverse
if (!require(here)) install.packages("here"); library(here) # relative file paths
```

Load the data from the your working directory

```{r message=FALSE}
# The chart data filepath

filenames <- list.files(path = here("data", "raw_data", "hot_100"), pattern = "*.csv")

filenames2 <- paste0(here("data", "raw_data", "hot_100"), "/", filenames)

# reading in the file names

df <-  filenames2 %>% map_df(~read_delim(., delim = "r"))
```


## Inspecting the data

When you click the **Render** button a document will be generated that includes both content and the output of embedded code. You can embed code like this:

```{r}
1 + 1
```

You can add options to executable code like this

```{r}
#| echo: false
2 * 2
```

The `echo: false` option disables the printing of code (only output is displayed).
